---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# gR2

This R package gR2 contains a function to compute the supervised and unsupervised sample generalized R square measures. The function also implements the K-lines clustering algorithm and allows an automatic choice of K for the unsupervised case. Statistical inference of the supervised and unsupervised population generalied R square measures is also included.

## Installation

You can install gR2 from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("lijy03/gR2")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# generate data from a bivariate normal mixture model
library(mvtnorm)
library(parallel)
K = 2 # number of components (lines)
p_s = c(0.5, 0.5) # proportions of components
mu_s = list(c(0,-2), c(0,2)) # mean vectors
Sigma_s = list(rbind(c(1,0.8),c(0.8,1)), rbind(c(1,0.8),c(0.8,1))) # covariance matrices
z = sample(1:K, size=n, prob=p_s, replace=T) # line memberships
data = matrix(0, nrow=n, ncol=2)
for (i in 1:K) {
  idx = which(z==i)
  data[idx,] = rmvnorm(n=length(idx), mean=mu_s[[i]], sigma=Sigma_s[[i]])
}
x = data[,1]
y = data[,2]

# plot the data
plot(x, y)

# supervised sample generalized R square
gR2(x, y, z) # without inference
gR2(x, y, z, inference=TRUE) # with inference

# unsupervised sample generalized R square
gR2(x, y, K=2) # with K specified, without inference
gR2(x, y, inference=TRUE) # without K specified, with inference
```

Please refer to the package [manual](https://github.com/lijy03/gR2/blob/master/gR2.pdf)
for a full list of arguments and detailed usage.
