---
output: github_document
---

## Installation

If you are using Linux or Windows, you can install gR2 from GitHub with:

```{r,eval=FALSE}
#install.packages("devtools")
devtools::install_github("lijy03/gR2")
```

If you are using macOS, you may encounter this error when trying to install gR2 with the above command:

clang: error: unsupported option '-fopenmp'

To resolve this issue, you can follow the instructions found here:

https://thecoatlessprofessor.com/programming/cpp/r-compiler-tools-for-rcpp-on-macos/, or

https://github.com/rmacoslib/r-macos-rtools.

Basically, what you need to do is download an macOS package (r-macos-rtools) and install it. Then, you should be able to install gR2 with devtools::install_github().

## Examples

### Simulate data:

```{r}
#Simulates data from a mixture of two bivariate normal distributions
simulateData<-function(seed=1){
  set.seed(seed)
  n=200 #Sample size
  K=2 #Number of components (lines)
  p_s=c(0.5,0.5) #Proportions of components
  mu_s=list(c(0,-2),c(0,2)) #mean vectors
  Sigma_s=list(rbind(c(1,0.8),c(0.8,1)),rbind(c(1,0.8),c(0.8,1))) #Covariance matrices
  z=sample(1:K,size=n,prob=p_s,replace=TRUE) #Line memberships
  data=matrix(0,nrow=n,ncol=2)
  for (i in 1:K){
    idx=which(z==i)
    data[idx,]=mvtnorm::rmvnorm(n=length(idx),mean=mu_s[[i]],sigma=Sigma_s[[i]])
  }
  return(cbind(data,z))
}

data<-simulateData(seed=7)
x<-data[,1]
y<-data[,2]
z<-data[,3]
```

### Typical uses of gR2():

```{r}
library(gR2)

#The following two lines make gR2 reproducible:
RNGkind("L'Ecuyer-CMRG")
set.seed(11)

#Specified scenario
result<-gR2(x,y,z) #No inference
result<-gR2(x,y,z,inference=TRUE) #Inference

#Unspecified scenario (K chosen)
result<-gR2(x,y,K=2) #No inference
result<-gR2(x,y,K=2,inference=TRUE) #Inference

#Unspecified scenario (K not chosen)
#result<-gR2(x,y) #No inference
result<-gR2(x,y,inference=TRUE) #Inference
```

### A more comprehensive list of uses of gR2():

```{r,eval=FALSE}
#Basic categories: specified, unspecified K chosen, unspecified K not chosen
#Inference: no inference, inference (general), inference (bivariate normal)
#If unspecified: MA, LM
#Total number of scenarios: 3 (specified) + 3 (unspecified K chosen, MA) + 3 (unspecified K not chosen, MA) + 6 (LM) = 15
#If specified + no inference, then output a list of one item: estimate.
#If specified + inference, then output a list of four items: estimate, conf.level, conf.int, and p.val.
#If unspecified + no inference, then output a list of three item: estimate, K, membership.
#If unspecified + inference, then output a list of six items: estimate, conf.level, conf.int, p.val, K, membership.

#Scenario 1: specified, no inference
#Output: a list of one item: estimate
result1<-gR2(x,y,z)
result1

#Scenario 2: specified, inference (general)
#Output: a list of four items: estimate, conf.level, conf.int, and p.val
result2<-gR2(x,y,z,inference=TRUE)
result2

#Scenario 3: specified, inference (bivariate normal)
#Output: a list of four items: estimate, conf.level, conf.int, and p.val
result3<-gR2(x,y,z,inference=TRUE,method="binorm")
result3

#Scenario 4: unspecified K chosen, no inference, MA
#Output: a list of three item: estimate, K, membership
result4<-gR2(x,y,K=2)
result4

#Scenario 5: unspecified K chosen, inference (general), MA
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result5<-gR2(x,y,K=2,inference=TRUE)
result5

#Scenario 6: unspecified K chosen, inference (bivariate normal), MA
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result6<-gR2(x,y,K=2,inference=TRUE,method="binorm")
result6

#Scenario 7: unspecified K not chosen, no inference, MA
#Output: a list of three item: estimate, K, membership
result7<-gR2(x,y)
result7

#Scenario 8: unspecified K not chosen, inference (general), MA
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result8<-gR2(x,y,inference=TRUE)
result8

#Scenario 9: unspecified K not chosen, inference (bivariate normal), MA
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result9<-gR2(x,y,inference=TRUE,method="binorm")
result9

#Scenario 10: unspecified K chosen, no inference, LM
#Output: a list of three item: estimate, K, membership
result10<-gR2(x,y,K=2,regressionMethod="LM")
result10

#Scenario 11: unspecified K chosen, inference (general), LM
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result11<-gR2(x,y,K=2,regressionMethod="LM",inference=TRUE)
result11

#Scenario 12: unspecified K chosen, inference (bivariate normal), LM
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result12<-gR2(x,y,K=2,regressionMethod="LM",inference=TRUE,method="binorm")
result12

#Scenario 13: unspecified K not chosen, no inference, LM
#Output: a list of three item: estimate, K, membership
result13<-gR2(x,y,regressionMethod="LM")
result13

#Scenario 14: unspecified K not chosen, inference (general), LM
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result14<-gR2(x,y,regressionMethod="LM",inference=TRUE)
result14

#Scenario 15: unspecified K not chosen, inference (bivariate normal), LM
#Output: a list of six items: estimate, conf.level, conf.int, p.val, K, membership
result15<-gR2(x,y,regressionMethod="LM",inference=TRUE,method="binorm")
result15
```
